Millions of Type Errors

### 2023-05-12 oopsla23/paper.tex
note wonky clientTimestamp

\Cref{f:records-per-hour} shows when data arrived across the whole dataset.

>>>>

\Cref{f:records-per-hour} shows when data arrived across the whole dataset.
FILL: currently clientTimestamp, which has caveats.
Unclear what timezone they are from.
Some records have a client timestamp much older than the server, up to 1 week behind.
Some are ahead of the server by a day.
Why?
Could be wrong local settings on the computer, or a delayed record due to lost
internet connection or closed laptop.
